Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-26 appendix.tex
u

>>>>

	\item [\xmark] Multicard DDP and single card training leads to different
		performance, regardless of the exact model of GPUs.
		%
		According to the observation, single card training leadss to a lower
		recall performance and a higher robustness score.
		%
		More efficient? This should be ok.
		%
		But be careful when doing ablation studies as this will greatly
		interfere with the conclusions.
